---
title: "Monitoring Report Extra Tables"
date: "`r format(Sys.time(), '%d %B, %Y')`"
header-includes: \usepackage{caption}
params:
  file_format: html
always_allow_html: yes
output:
  html_document:
    toc: true
    toc_depth: 4
  pdf_document:
    toc: true
    number_sections: true
  word_document:
    toc: true
---

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE,
                      message=FALSE, warning=FALSE)


library(rlang)
library(dplyr)
library(kableExtra)

if (!exists("fileFormat")) fileFormat <- params$file_format
```

```{css echo=FALSE}
/* Define a margin before h2 element */
h2,h3,h4  {
  margin-top: 6em;
}

/* Define a margin after every first p elements */
p:first-of-type {
  margin-bottom: 3em;
}
``` 

\captionsetup[table]{labelformat=empty}

## Table Monitoring Period Emissions/Removals

```{r echo = FALSE}
TableMPEmRems <- createTable_MPEmRems(MR_Values)
#TableMPEmRems["3", "Year"] <- cell_spec(TableMPEmRems["3", "Year"], color = "black", background = "lightgreen")
TableMPEmRems %>%
  kable(fileFormat, caption = "Monitoring Report Table Monitoring Report Emmission/Removals", digits = 4) %>%
  kable_styling(
    latex_options = c("hold_position", "scale_down")
  ) %>%  
  row_spec(0, color = "black", background = "lightgreen") 
  
  
```



## Estimation of emissions by source and removals by enhancements included in the ER Program's scope
### Monitoring Period, Year 2019, Net Emissions/Removals
$$
\begin{align}
ER_{2019} &= ER_{Defor,2019} + ER_{FDeg,2019} + ER_{Enh,2019} \\
\end{align}
$$


### Deforestation
$$ 
ER_{Def,2019} = ER_{Def,2019,Upland} + ER_{Def,2019,Lowland}
$$

#### Monitoring Period, Year 2019, Deforestation Upland 

$$ 
\begin{align}
ER_{Def,2019,Upland} &= AD_{Def,2019,Upland} \times  EF_{Def,Upland} \\
  &= `r MonitoredValues$year1$DeforAreaUp` \times  `r EFDeforUp`\\
  &= `r MonitoredValues$year1$DeforAreaUp * EFDeforUp`
\end{align}
$$



```{r echo = TRUE, prompt = TRUE}
MonitoredValues$year1$DeforAreaUp
EFDeforUp
MonitoredValues$year1$DeforAreaUp * EFDeforUp
```


#### Monitoring Period, Year 2019, Deforestation Lowland 

$$ 
\begin{align}
ER_{Def,2019,Lowland} &= AD_{Def,2019,Lowland} \times  EF_{Def,Lowland} \\
  &= `r MonitoredValues$year1$DeforAreaLow` \times `r EFDeforLow` \\
  &= `r MonitoredValues$year1$DeforAreaLow * EFDeforLow`
\end{align}
$$



```{r echo = TRUE, prompt = TRUE}
MonitoredValues$year1$DeforAreaLow
EFDeforLow
MonitoredValues$year1$DeforAreaLow * EFDeforLow
```


#### Monitoring Period, Year 2019, Total Deforestation

$$ 
\begin{align}
ER_{Def,2019} &= `r formatDecimal(MonitoredValues$year1$DeforAreaUp * EFDeforUp)`
  +  `r formatDecimal(MonitoredValues$year1$DeforAreaLow * EFDeforLow)`  \\
  &= `r formatDecimal((MonitoredValues$year1$DeforAreaUp * EFDeforUp) + (MonitoredValues$year1$DeforAreaLow * EFDeforLow))`
\end{align}
$$



```{r echo = TRUE, prompt = TRUE}
ER_DEF_2019 <- (MonitoredValues$year1$DeforAreaUp * EFDeforUp) + (MonitoredValues$year1$DeforAreaLow * EFDeforLow)
ER_DEF_2019
```

### Forest Degradation

$$ 
\begin{align}
ER_{FDeg,2019} &= ER_{NFH,2019,vol} + ER_{NFH,2019,fell} + ER_{NFF,2019} + ER_{FSW,2019} 
\end{align}
$$

#### Monitoring Period, Year 2019, Forest Degradation from native forest timber harvest (felling volumes)

$$ 
\begin{align}
AD_{NFH,2019,vol} &= `r MonitoredValues$year1$FDegFellVol` \\
EF_{Felling}         &= `r EFFelling` \\
EF_{Damage}          &= `r EFDamage` \\ 
EF_{Infrastructure}  &= `r EFInfrastructure` \\
EF_{NFHvol} &= TEF = EF_{Felling} + EF_{Damage} + EF_{Infrastructure} \\
    &= `r EFFelling`+ `r EFDamage` + `r EFInfrastructure` \\
    &= `r TEF` \\
ER_{NFH,2019,vol}  &= AD_{NFH,2019,vol} \times EF_{NFHvol} \times \frac{44}{12} \\
  &=   ( `r MonitoredValues$year1$FDegFellVol` \times `r TEF` ) \times \frac{44}{12} \\
  &= `r ConvCarbonToCO2e(MonitoredValues$year1$FDegFellVol * TEF) `
\end{align}
$$



```{r echo = TRUE, prompt = TRUE}
MonitoredValues$year1$FDegFellVol
EFFelling 
EFDamage 
EFInfrastructure
TEF
ConvCarbonToCO2e(MonitoredValues$year1$FDegFellVol * TEF)

```
#### Monitoring Period, Year 2019, Forest Degradation from native forest timber harvest (felling area)
$$ 
\begin{align}
AD_{NFH,2019,area} &= `r MonitoredValues$year1$FDegFellArea$area_ha` \\
AD_{NFH,2019,age}  &= `r MonitoredValues$year1$FDegFellArea$age_yrs` \\
MAIC_{NFHfell}    &= `r MAICFell` \\
ER_{NFH,2019,fell} &=  AD_{NFH,2019,area} \times AD_{NFH,2019,age} \times MAIC_{NFHfell} \times \frac{44}{12} \times -1\\
                  &= ( `r MonitoredValues$year1$FDegFellArea$area_ha` \times 
     `r MonitoredValues$year1$FDegFellArea$age_yrs` \times `r MAICFell` ) \times 
     \frac{44}{12} \times -1\\
                  &= `r ConvCarbonToCO2e(MonitoredValues$year1$FDegFellArea$area_ha * MonitoredValues$year1$FDegFellArea$age_yrs * MAICFell) * (-1)`
\end{align}
$$



```{r echo = TRUE, prompt = TRUE}
MonitoredValues$year1$FDegFellArea$area_ha
MonitoredValues$year1$FDegFellArea$age_yrs
MAICFell
ConvCarbonToCO2e(MonitoredValues$year1$FDegFellArea$area_ha * MonitoredValues$year1$FDegFellArea$age_yrs * MAICFell) * (-1)

```
#### Monitoring Period, Year 2019, Forest Degradation from closed to open native forest

$$ 
\begin{align}
AD_{NFDeg,2019} &= `r MonitoredValues$year1$NFDegArea` \\
ABGBC_{NFDeg} &= `r EFNFDeg` \\
RootToShootRatio_{TropRain} &= `r RootToShootTropRain` \\
ER_{NFF,2019}  &= AD_{NFDeg,2019} \times ABGBC_{NFDeg} \times (1 + RootToShootRatio_{TropRain}) \times 0.47 \times \frac{44}{12}\\
  &= `r MonitoredValues$year1$NFDegArea` \times `r EFNFDeg` \times (1 + `r RootToShootTropRain`)  
      \times 0.47 \times \frac{44}{12}\\
  &= `r ConvBiomassToCO2e(MonitoredValues$year1$NFDegArea * EFNFDeg * (1 + RootToShootTropRain))`
\end{align}
$$



```{r echo = TRUE, prompt = TRUE}
MonitoredValues$year1$NFDegArea
EFNFDeg
RootToShootTropRain
MonitoredValues$year1$NFDegArea * EFNFDeg * (1 + RootToShootTropRain)
ConvBiomassToCO2e(MonitoredValues$year1$NFDegArea * EFNFDeg * (1 + RootToShootTropRain))
```
#### Monitoring Period, Year 2019, Forest Degradation from softwood fire
```{r echo = FALSE, prompt = FALSE}
# Estimate AGB
AGB <- MonitoredValues$year1$FDegBurnData$age_yrs * (MAIBsw / (1 + RootToShootDryLandSmall))
# Estimate BGB
BGB <- MonitoredValues$year1$FDegBurnData$age_yrs * (MAIBsw * RootToShootDryLandSmall)
```

$$ 
\begin{align}
AD_{FDegBurnData,2019,age,i}    &= `r MonitoredValues$year1$FDegBurnData$age_yrs` \\
AD_{FDegBurnData,2019,area,i}   &= `r MonitoredValues$year1$FDegBurnData$area_ha` \\
MAIB_{sw}                       &= `r MAIBsw` \\
RootToShootRatio_{DryLandSmall} &= `r RootToShootDryLandSmall` \\
CombustFactor                   &= `r CombustFactor` \\
GWP_{CO_2}  &= `r GWPCO2` \\
GWP_{CH_4}  &= `r GWPCH4` \\
GWP_{N_2O}  &= `r GWPN2O` \\
EF_{CO_2}   &= `r EFCO2` \\
EF_{CH_4}   &= `r EFCH4` \\
EF_{N_2O}   &= `r EFN2O` \\
AGB_{i} &= AD_{FDegBurnData,2019,age,i} \times \frac{MAIB_{sw}}{1 + RootToShootRatio_{DryLandSmall}} \\
    &= \{`r MonitoredValues$year1$FDegBurnData$age_yrs`\} \times \frac{`r MAIBsw`}{1 + `r RootToShootDryLandSmall`} \\
BGB_{i} &= AD_{FDegBurnData,2019,age,i} \times MAIB_{sw} \times RootToShootRatio_{DryLandSmall} \\
    &= \{`r MonitoredValues$year1$FDegBurnData$age_yrs`\} \times `r MAIBsw` \times `r RootToShootDryLandSmall`\\
EmCO_2AGB_{i} &= AD_{FDegBurnData,2019,area,i} \times AGB_{i} \times CombustFactor \times GWP_{CO_2} \times EF_{CO_2}  \times 0.001 \\
             &= \{`r formatDecimal(MonitoredValues$year1$FDegBurnData$area_ha)`\} \\
             &  \times `r formatDecimal(AGB)` \\
             &  \times `r formatDecimal(CombustFactor)` 
                \times `r GWPCO2` \times `r EFCO2`  \times `r 0.001` \\
\sum EmCO_2AGB_{i} &= `r sum(MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPCO2 * EFCO2  * 0.001)`\\
EmCO_2BGB_{i} &= AD_{FDegBurnData,2019,area,i} \times BGB_{i} \times CombustFactor \times GWP_{CO_2} \times EF_{CO_2}  \times 0.001 \\
             &= \{`r formatDecimal(MonitoredValues$year1$FDegBurnData$area_ha)`\} \\
             &  \times `r formatDecimal(BGB)` \\
             &  \times `r formatDecimal(CombustFactor)` 
                \times `r GWPCO2` \times `r EFCO2`  \times `r 0.001` \\
\sum EmCO_2BGB_{i} &= `r sum(MonitoredValues$year1$FDegBurnData$area_ha * BGB * CombustFactor * GWPCO2 * EFCO2  * 0.001)`\\
{EmCH_{4}}_i    &= AD_{FDegBurnData,2019,area,i} \times AGB_{i} \times CombustFactor \times GWP_{CH_4} \times EF_{CH_4} \times 0.001  \\
             &= \{`r formatDecimal(MonitoredValues$year1$FDegBurnData$area_ha)`\} \\
             &  \times `r formatDecimal(AGB)` \\
             &  \times `r formatDecimal(CombustFactor)` 
                \times `r GWPCH4` \times `r EFCH4` \times `r 0.001` \\
\sum {EmCH_{4}}_i &= `r sum(MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPCH4 * EFCH4 * 0.001)` \\
{EmN_{2}O}_i    &= AD_{FDegBurnData,2019,area,i} \times AGB_{i} \times CombustFactor \times GWP_{N_2O} \times EF_{N_2O} \times 0.001  \\
             &= \{`r formatDecimal(MonitoredValues$year1$FDegBurnData$area_ha)`\} \\
             &  \times `r formatDecimal(AGB)` \\
             &  \times `r formatDecimal(CombustFactor)` 
                \times `r GWPN2O` \times `r EFN2O` \times `r 0.001` \\
\sum {EmN_{2}O}_i &= `r sum(MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPN2O * EFN2O * 0.001)` \\
ER_{FSW,2019}&=  \sum EmCO_2AGB_{i} + \sum EmCO_2BGB_{i}  + \sum {EmCH_{4}}_i + \sum {EmN_{2}O}_i \\
             &= `r sum(MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPCO2 * EFCO2  * 0.001)`
               + `r sum(MonitoredValues$year1$FDegBurnData$area_ha * BGB * CombustFactor * GWPCO2 * EFCO2  * 0.001)`
               + `r sum(MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPCH4 * EFCH4 * 0.001)` 
               + `r sum(MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPN2O * EFN2O * 0.001)` \\
               &= `r sum(MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPCO2 * EFCO2  * 0.001) + sum(MonitoredValues$year1$FDegBurnData$area_ha * BGB * CombustFactor * GWPCO2 * EFCO2  * 0.001) + sum(MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPCH4 * EFCH4 * 0.001)  + sum(MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPN2O * EFN2O * 0.001)` \\
\end{align}
$$



```{r echo = TRUE, prompt = TRUE}


MonitoredValues$year1$FDegBurnData$age_yrs
MAIBsw
RootToShootDryLandSmall
MonitoredValues$year1$FDegBurnData$area_ha
CombustFactor
GWPCO2
GWPCH4
GWPN2O
EFCO2
EFCH4
EFN2O

# Estimate AGB
AGB <- MonitoredValues$year1$FDegBurnData$age_yrs * (MAIBsw / (1 + RootToShootDryLandSmall))
# Estimate BGB
BGB <- MonitoredValues$year1$FDegBurnData$age_yrs * (MAIBsw * RootToShootDryLandSmall)
# CO2 ABG emissions
EmCO2AGB <- MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPCO2 * EFCO2  * 0.001
# CO2 BGB emissions
EmCO2BGB <- MonitoredValues$year1$FDegBurnData$area_ha * BGB * CombustFactor * GWPCO2 * EFCO2 * 0.001
# CH4 ABG emissions
EmCH4 <- MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPCH4 * EFCH4 * 0.001
# N_2O (above-ground biomass)
EmN2O <- MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPN2O  * EFN2O * 0.001
# sum emissions for each gas and put into dataframe
sum(sum(EmCO2AGB), sum(EmCO2BGB), sum(EmCH4), sum(EmN2O))


```
#### Monitoring Period, Year 2019, Total Forest Degradation

$$ 
\begin{align}
ER_{FDeg,2019} &= `r ConvCarbonToCO2e(MonitoredValues$year1$FDegFellVol * TEF)` 
  + (`r ConvCarbonToCO2e(MonitoredValues$year1$FDegFellArea$area_ha * MonitoredValues$year1$FDegFellArea$age_yrs * MAICFell) * -1`)
  + `r ConvBiomassToCO2e(MonitoredValues$year1$NFDegArea * EFNFDeg * (1 + RootToShootTropRain))`
  + `r sum(MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPCO2 * EFCO2  * 0.001) + sum(MonitoredValues$year1$FDegBurnData$area_ha * BGB * CombustFactor * GWPCO2 * EFCO2  * 0.001) + sum(MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPCH4 * EFCH4 * 0.001)  + sum(MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPN2O * EFN2O * 0.001)` \\
  &= `r formatDecimal(ConvCarbonToCO2e(MonitoredValues$year1$FDegFellVol * TEF) + ( ConvCarbonToCO2e(MonitoredValues$year1$FDegFellArea$area_ha * MonitoredValues$year1$FDegFellArea$age_yrs * MAICFell) * -1) +  ConvBiomassToCO2e(MonitoredValues$year1$NFDegArea * EFNFDeg * (1 + RootToShootTropRain)) + sum(MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPCO2 * EFCO2  * 0.001) + sum(MonitoredValues$year1$FDegBurnData$area_ha * BGB * CombustFactor * GWPCO2 * EFCO2  * 0.001) + sum(MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPCH4 * EFCH4 * 0.001)  + sum(MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPN2O * EFN2O * 0.001))`
\end{align}
$$


```{r echo = TRUE, prompt = FALSE}

ER_FDEG_2019 <- ConvCarbonToCO2e(MonitoredValues$year1$FDegFellVol * TEF) +
(ConvCarbonToCO2e(MonitoredValues$year1$FDegFellArea$area_ha * MonitoredValues$year1$FDegFellArea$age_yrs * MAICFell) * -1) +
ConvBiomassToCO2e(MonitoredValues$year1$NFDegArea * EFNFDeg * (1 + RootToShootTropRain)) +
sum(MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPCO2 * EFCO2  * 0.001) +
sum(MonitoredValues$year1$FDegBurnData$area_ha * BGB * CombustFactor * GWPCO2 * EFCO2  * 0.001) +
sum(MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPCH4 * EFCH4 * 0.001)  +
sum(MonitoredValues$year1$FDegBurnData$area_ha * AGB * CombustFactor * GWPN2O * EFN2O * 0.001)
ER_FDEG_2019

```



### Removals by Enhancments
$$
ER_{Enh,2019} = ER_{FPln,2019} + Rem_{AR,2019}
$$

#### Monitoring Period, Year 2019, Emission/Removals from forest plantation Hardwood and Softwood
$$
\begin{align}
ER_{FPln,2019} &= ER_{FPln,2019,Hardwood} + ER_{FPln,2019,Softwood}
\end{align}
$$

#### Monitoring Period, Year 2019, Emission/Removals from forest plantation Hardwood
$$
\begin{align}
ER_{FPln,2019,Hardwood} &= Em_{FPln,2019,Hardwood} + Rem_{FPln,2019,Hardwood}
\end{align}
$$

#### Monitoring Period, Year 2019, Emissions from forest plantation Hardwood
$$
\begin{align}
Em_{FPln,2019,Hardwood} &= (AD_{FPln,2019,vol,hardwoord} \times BiomassConvExpansion_{Hardwood} \\
  & + AD_{FPln,2019,vol,hardwoord} \times BiomassConvExpansion_{Hardwood} \times RootToShoot_{TropRain}) \\
  & \times 0.47 \times \frac{44}{12} \\
  &= (`r MonitoredValues$year1$FPlnVolHarvHwd` \times `r BiomassConvExpansionHW` 
    + `r MonitoredValues$year1$FPlnVolHarvHwd` \times `r BiomassConvExpansionHW` \times `r RootToShootTropRain`)
    \times 0.47 \times \frac{44}{12} \\
  &= `r (MonitoredValues$year1$FPlnVolHarvHwd * BiomassConvExpansionHW 
  + MonitoredValues$year1$FPlnVolHarvHwd * BiomassConvExpansionHW * RootToShootTropRain) * 0.47 * (44/12)`
\end{align}
$$

```{r echo = TRUE, prompt = TRUE}
#' Forest Plantations - Emissions from Hardwood Plantations
MonitoredValues$year1$FPlnVolHarvHwd
BiomassConvExpansionHW
RootToShootTropRain
  
#CalcEstEmFPlnHwd
Em_FPln_2019_Hardwood <- ConvBiomassToCO2e(MonitoredValues$year1$FPlnVolHarvHwd * BiomassConvExpansionHW + MonitoredValues$year1$FPlnVolHarvHwd * BiomassConvExpansionHW * RootToShootTropRain)
Em_FPln_2019_Hardwood
```

#### Monitoring Period, Year 2019, Removals from forest plantation Hardwood
```{r echo = FALSE, prompt = FALSE}
MAIBhw <- MAIVhw * BiomassConvExpansionIncHW * (1 + RootToShootTropRain)
```

$$
\begin{align}
AD_{FPln,2019,age,Hardwood}   &= `r MonitoredValues$year1$FPlnAreaPlantHwd$age_yrs` \\
AD_{FPln,2019,area,Hardwood}  &= `r MonitoredValues$year1$FPlnAreaPlantHwd$area_ha` \\
MAIV_{Hardwood}               &= `r MAIVhw` \\
BiomassConvExpansion_{IncHW}  &= `r BiomassConvExpansionIncHW` \\
RootToShootRatio_{TropRain}   &= `r RootToShootTropRain` \\
MAIB_{Hardwood}               &= MAIV_{Hardwood} \times BiomassConvExpansion_{IncHW} \times (1 + RootToShoot_{TropRain}) \\
                              &= `r MAIVhw` \times `r BiomassConvExpansionIncHW` \times (1 + `r RootToShootTropRain`) \\
                              &= `r MAIVhw * BiomassConvExpansionIncHW * (1 + RootToShootTropRain)` \\
Rem_{FPln,2019,Hardwood} &=  AD_{FPln,2019,age,Hardwood} \times AD_{FPln,2019,area,Hardwood} \times MAIB_{Hardwood} \times 0.47 \times \frac{44}{12} \times -1 \\
  &=  `r MonitoredValues$year1$FPlnAreaPlantHwd$age_yrs` \times `r MonitoredValues$year1$FPlnAreaPlantHwd$area_ha` \times `r MAIBhw` \times 0.47 \times \frac{44}{12} \times -1 \\
  &=  `r MonitoredValues$year1$FPlnAreaPlantHwd$age_yrs * MonitoredValues$year1$FPlnAreaPlantHwd$area_ha * MAIBhw * 0.47 * (44/12) * -1`
\end{align}
$$

```{r echo = TRUE, prompt = TRUE}
#' Forest Plantations - Removals from Hardwood Plantations
MonitoredValues$year1$FPlnAreaPlantHwd$area_ha
MAIVhw
BiomassConvExpansionIncHW
RootToShootTropRain
MonitoredValues$year1$FPlnAreaPlantHwd$age_yrs
  
#CalcEstRemFPlnHwd
MAIBhw <- MAIVhw * BiomassConvExpansionIncHW * (1 + RootToShootTropRain)
MAIBhw

Rem_FPln_2019_Hardwood <- ConvBiomassToCO2e(MonitoredValues$year1$FPlnAreaPlantHwd$age_yrs * MonitoredValues$year1$FPlnAreaPlantHwd$area_ha * MAIBhw) * -1
Rem_FPln_2019_Hardwood

```
#### Monitoring Period, Year 2019, Net ER from forest plantation Hardwood
$$
\begin{align}
ER_{FPln,2019,Hardwood} &= `r Em_FPln_2019_Hardwood` + `r Rem_FPln_2019_Hardwood` \\
   &= `r Em_FPln_2019_Hardwood + Rem_FPln_2019_Hardwood`
\end{align}
$$

```{r echo = TRUE, prompt = TRUE}
ER_FPln_2019_Hardwood <- Em_FPln_2019_Hardwood + Rem_FPln_2019_Hardwood
ER_FPln_2019_Hardwood

```    
#### Monitoring Period, Year 2019, Emission/Removals from forest plantation Softwood
$$
\begin{align}
ER_{FPln,2019,Softwood} &= Em_{FPln,2019,Softwood} + Rem_{FPln,2019,Softwood}
\end{align}
$$

#### Monitoring Period, Year 2019, Emissions from forest plantation Softwood
$$
\begin{align}
AD_{FPln,2019,vol,Softwood}   &= `r MonitoredValues$year1$FPlnVolHarvSwd` \\
RecoveryRate_{Softwood}       &= `r RecoveryRateSW` \\
WoodDensity_{Softwood}        &= `r WoodDensitySW` \\
RootToShootRatio_{DryLandBig} &= `r RootToShootDryLandBig` \\
Em_{FPln,2019,Softwood} &= (AD_{FPln,2019,vol,Softwood} \times \frac{1}{RecoveryRate_{Softwood}} \times WoodDensity_{Softwood} \\
   & + AD_{FPln,2019,vol,Softwood} \times \frac{1}{RecoveryRate_{Softwood}} \\
   & \times WoodDensity_{Softwood} \times RootToShootRatio_{DryLandBig}) \\
   & \times  0.47 \times \frac{44}{12} \\
   &= (`r MonitoredValues$year1$FPlnVolHarvSwd` \times \frac{1}{`r RecoveryRateSW`} \times `r WoodDensitySW` \\
   & +`r MonitoredValues$year1$FPlnVolHarvSwd` \times \frac{1}{`r RecoveryRateSW`} \times `r WoodDensitySW` \times  
      `r RootToShootDryLandBig`) \times  0.47 \times \frac{44}{12} \\
   &= `r (MonitoredValues$year1$FPlnVolHarvSwd * (1/RecoveryRateSW) * WoodDensitySW +
MonitoredValues$year1$FPlnVolHarvSwd * (1/RecoveryRateSW) * WoodDensitySW *  
                RootToShootDryLandBig) * 0.47 * (44/12)`
\end{align}
$$

```{r echo = TRUE, prompt = TRUE}
#' Forest Plantations - Emissions from Softwood Plantations
MonitoredValues$year1$FPlnVolHarvSwd
RecoveryRateSW
WoodDensitySW
RootToShootDryLandBig

#CalcEstEmFPlnSwd
Em_FPln_2019_Softwood <- ConvBiomassToCO2e((MonitoredValues$year1$FPlnVolHarvSwd * (1/RecoveryRateSW) * WoodDensitySW) +
(MonitoredValues$year1$FPlnVolHarvSwd * (1/RecoveryRateSW) * WoodDensitySW * RootToShootDryLandBig))
Em_FPln_2019_Softwood
```

#### Monitoring Period, Year 2019, Removals from forest plantation Softwood
```{r echo = FALSE, prompt = FALSE}
MAICsw <- ConvBiomassToCarbon(MAIBsw)
```

$$
\begin{align}
AD_{FPln,2019,age,Softwood}  &= `r MonitoredValues$year1$FPlnAreaPlantSwd$age_yrs` \\
AD_{FPln,2019,area,Softwood} &= `r MonitoredValues$year1$FPlnAreaPlantSwd$area_ha` \\
MAIB_{Softwood}              &= `r MAIBsw` \\
MAIC_{Softwood}              &= MAIB_{softwood} \times 0.47 \\
                             &= `r MAIBsw` \times 0.47 \\
                             &= `r MAIBsw * 0.47` \\
Rem_{FPln,2019,Softwood}     &= AD_{FPln,2019,age,Softwood}
  \times AD_{FPln,2019,area,Softwood} \times MAIC_{Softwood} \times \frac{44}{12} \times -1\\
                             &= `r MonitoredValues$year1$FPlnAreaPlantSwd$age_yrs`
  \times `r MonitoredValues$year1$FPlnAreaPlantSwd$area_ha`  \times `r MAICsw` \times \frac{44}{12} \times -1\\
                             &= `r MonitoredValues$year1$FPlnAreaPlantSwd$age_yrs * MonitoredValues$year1$FPlnAreaPlantSwd$area_ha * MAICsw * (44/12) * -1`
\end{align}
$$

```{r echo = TRUE, prompt = TRUE}
#' Forest Plantations - Removals from Softwood Plantations
MAIBsw
MonitoredValues$year1$FPlnAreaPlantSwd$area_ha
MonitoredValues$year1$FPlnAreaPlantSwd$age_yrs

# CalcEstRemFPlnSwd 
# Calc mean annual increment C for volume m^3
MAICsw <- ConvBiomassToCarbon(MAIBsw)
MAICsw
Rem_FPln_2019_Softwood <-ConvCarbonToCO2e(MonitoredValues$year1$FPlnAreaPlantSwd$age_yrs * MonitoredValues$year1$FPlnAreaPlantSwd$area_ha * MAICsw) * -1
Rem_FPln_2019_Softwood
```

#### Monitoring Period, Year 2019, Net ER from forest plantation Softwood
$$
\begin{align}
ER_{FPln,2019,Softwood} 
        &= `r Em_FPln_2019_Softwood` + (`r Rem_FPln_2019_Softwood`) \\
        &= `r Em_FPln_2019_Softwood + Rem_FPln_2019_Softwood`
\end{align}
$$

```{r echo = TRUE, prompt = FALSE}

Em_FPln_2019_Softwood
Rem_FPln_2019_Softwood

ER_FPln_2019_Softwood <-  Em_FPln_2019_Softwood + Rem_FPln_2019_Softwood 
ER_FPln_2019_Softwood

```
#### Monitoring Period, Year 2019, Total Emission/Removals from forest plantation Hardwood and Softwood
$$
\begin{align}
ER_{FPln,2019} &= `r ER_FPln_2019_Hardwood` + `r ER_FPln_2019_Softwood` \\
               &= `r ER_FPln_2019_Hardwood +  ER_FPln_2019_Softwood`
\end{align}
$$
```{r echo = TRUE, prompt = FALSE}
ER_FPln_2019 <-ER_FPln_2019_Hardwood +  ER_FPln_2019_Softwood
ER_FPln_2019
```

#### Monitoring Period, Year 2019, Removals from Afforestation/Reforestation
```{r echo = FALSE, prompt = FALSE}
MAIC <-MAIVar * BiomassConvExpansionARefor * (1 + RootToShootTropRain)
```
ghdfg
$$
\begin{align}
AD_{AR,2019,age,i}          &= `r MonitoredValues$year1$AReforArea$age_yrs` \\
AD_{AR,2019,area,i}         &= `r MonitoredValues$year1$AReforArea$area_ha` \\
MAIV_{AR}                   &= `r MAIVar` \\
BiomassConvExpansion_{AR}   &= `r BiomassConvExpansionARefor` \\
RootToShootRatio_{TropRain} &= `r RootToShootTropRain` \\
MAIC_{AR}                   &= MAIV_{AR} \times  BiomassConvExpansion_{AR} \times (1 + RootToShootRatio_{TropTain}) \\
                            &= `r MAIVar` \times  `r BiomassConvExpansionARefor` \times (1 + `r RootToShootTropRain`) \\
                            &= `r MAIVar * BiomassConvExpansionARefor * (1 + RootToShootTropRain)` \\
Rem_{AR,2019}  &= AD_{AR,2019,age} \times AD_{AR,2019,area} \times MAIC_{AR} \times 0.47 \times \frac{44}{12} \times -1 \\
               &= `r MonitoredValues$year1$AReforArea$age_yrs` \times 
                  `r MonitoredValues$year1$AReforArea$area_ha` \times 
                  `r MAIC` \times `r BiomassConvExpansionARefor` \times (1 + `r RootToShootTropRain`) \times 
                  0.47 \times \frac{44}{12} \times -1 \\
               &= `r MonitoredValues$year1$AReforArea$age_yrs *
                      MonitoredValues$year1$AReforArea$area_ha * MAIC * 0.47 * (44/12) * (-1)`
\end{align}
$$


```{r echo = TRUE, prompt = TRUE}
MonitoredValues$year1$AReforArea$age_yrs
MAIVar
BiomassConvExpansionARefor
RootToShootTropRain
MonitoredValues$year1$AReforArea$area_ha
 

MAIC <-MAIVar * BiomassConvExpansionARefor * (1 + RootToShootTropRain)
MAIC

Rem_AR_2019 <- ConvBiomassToCO2e(MonitoredValues$year1$AReforArea$age_yrs * 
                    MonitoredValues$year1$AReforArea$area_ha * MAIC * (-1)) 
Rem_AR_2019
  
```
#### Monitoring Period, Year 2019, Total Emission/Removals from enhancements
$$
\begin{align}
ER_{Enh,2019} &= `r ER_FPln_2019` + (`r Rem_AR_2019`) \\
              &= `r ER_FPln_2019 + Rem_AR_2019`
\end{align}
$$

```{r echo = TRUE, prompt = TRUE}
ER_Enh_2019 <- ER_FPln_2019 + Rem_AR_2019
ER_Enh_2019
```
### Monitoring Period, Year 2019, Net Emissions/Removals
$$
\begin{align}
ER_{2019} &= ER_{Defor,2019} + ER_{FDeg,2019} + ER_{Enh,2019} \\
          &= `r ER_DEF_2019` + `r ER_FDEG_2019` + `r ER_Enh_2019` \\
          &= `r ER_DEF_2019 + ER_FDEG_2019 + ER_Enh_2019` 
\end{align}
$$

```{r echo = TRUE, prompt = TRUE}
ER_2019 <- ER_DEF_2019 + ER_FDEG_2019 + ER_Enh_2019
ER_2019
```